Geostrophic currents

### 2019-04-03 geostrophic_currents.Rmd
updated: Require BC data

```{r}
library(ncdf4) 
library(data.table) 
library(tidyverse) 
library(reshape2) 
library(plyr) 
library(lubridate)
library(stringr)

@@

ncread(nc.dir, csv.dir)
```

@@

AVISO <- AVISO %>%
  dplyr::group_by(lon, lat) %>%
  dplyr::summarise(u = mean(u, na.rm = TRUE),
                   v = mean(v, na.rm = TRUE),
                   mean.adt = mean(adt, na.rm = TRUE),
                   mean.sla = mean(sla, na.rm = TRUE)) %>%
  dplyr::ungroup() %>%
  dplyr::mutate(velocity = sqrt((v^2) + (u^2)),
                eke = 0.5 * (u^2 + v^2),
                arrow_size = ((abs(u * v) / max(abs(u * v))) + 0.3) / 6)

save(AVISO, file = "Data/AVISO.RData")
```

>>>>

```{r}
library(ncdf4) 
library(data.table) 
library(tidyverse) 
library(reshape2) 
library(plyr) 
library(lubridate)
library(stringr)
library(doMC); doMC::registerDoMC(cores = 1)

@@

ncread(nc.dir, csv.dir)

# coords <- c(-35, -20, 10, 20) # this is the BC
```

@@

AVISO <- AVISO %>%
  dplyr::group_by(lon, lat, date) %>%
  dplyr::summarise(u = mean(u, na.rm = TRUE),
                   v = mean(v, na.rm = TRUE),
                   mean.adt = mean(adt, na.rm = TRUE),
                   mean.sla = mean(sla, na.rm = TRUE)) %>%
  dplyr::ungroup() %>%
  dplyr::mutate(velocity = sqrt((v^2) + (u^2)),
                eke = 0.5 * (u^2 + v^2))

AVISO_test1 <- AVISO%>%
  dplyr::mutate(lon = round(lon, 0),
                lat = round(lat, 0)) %>%
  dplyr::group_by(lon, lat) %>%
  dplyr::summarise(u = mean(u, na.rm = TRUE),
                   v = mean(v, na.rm = TRUE),
                   velocity = mean(velocity, na.rm = TRUE)) %>%
  dplyr::ungroup()

plot1 <- ggplot(AVISO_test1, aes(x = lon, y = lat)) +
    geom_raster(aes(fill = velocity)) +
    scale_fill_gradientn(colours = rev(rainbow(7, end = 4/6)),
                         space = "Lab", limits = c(0, 1.45),
                         guide = guide_colorbar(title = expression(Velocity~(m~s^{-1})),
                                                position = "bottom",
                                                direction = "horizontal",
                                                barheight = unit(2, units = "mm"),
                                                barwidth = unit(50, units = "mm"),
                                                draw.ulim = F,
                                                title.position = 'top',
                                                title.hjust = 0.5,
                                                label.hjust = 0.5)) +
  geom_segment(data = vec,
               aes(xend = lon + u * current_uv_scalar,
                   yend = lat + v * current_uv_scalar, alpha = velocity),
               arrow = arrow(angle = 20, length = unit(0.1, "cm"), type = "open"), size = 0.35, show.legend = FALSE) +
  scale_alpha_continuous(range = c(0, 1.0))

```
